ISYE 6501

### 2022-09-28 hw5-1/submission.Rmd
Submission.Rmd

@@

for (ntree_i in seq(30,130,10)) {
  for (mtry_i in seq(2,6,1)) {
    #RMSE on each CV Fold for ntree_i,mtry_i
    rmse_cv_all = lapply(seq(1:5), function(fold) 
      CV_rf_func(test_fold = fold, ntree1 = ntree_i, mtry1 = mtry_i))
    rmse_cv_df = do.call(rbind.data.frame, rmse_cv_all)
    rmse_cv1 = mean(unlist(rmse_cv_df[,1]))
    rmse_cv2 = mean(unlist(rmse_cv_df[,2]))
    rmse_cv3 = mean(unlist(rmse_cv_df[,3]))
    print (paste("For tree:",ntree_i,"mtry:",mtry_i))
    rmse_list1 = c(rmse_list1, rmse_cv1)
    rmse_list2 = c(rmse_list2, rmse_cv2)
    rmse_list3 = c(rmse_list3, rmse_cv3)
    ntree_list = c(ntree_list, ntree_i)
    mtry_list = c(mtry_list, mtry_i)
}
}
```

@@

>>>>

**Q10.1**

@@

for (ntree_i in seq(30,130,10)) {
  for (mtry_i in seq(2,6,1)) {
    #RMSE on each CV Fold for ntree_i,mtry_i
    rmse_cv_all = lapply(seq(1:5), function(fold) 
      CV_rf_func(test_fold = fold, ntree1 = ntree_i, mtry1 = mtry_i))
    rmse_cv_df = do.call(rbind.data.frame, rmse_cv_all)
    rmse_cv1 = mean(unlist(rmse_cv_df[,1]))
    rmse_cv2 = mean(unlist(rmse_cv_df[,2]))
    rmse_cv3 = mean(unlist(rmse_cv_df[,3]))
    #print (paste("For tree:",ntree_i,"mtry:",mtry_i))
    rmse_list1 = c(rmse_list1, rmse_cv1)
    rmse_list2 = c(rmse_list2, rmse_cv2)
    rmse_list3 = c(rmse_list3, rmse_cv3)
    ntree_list = c(ntree_list, ntree_i)
    mtry_list = c(mtry_list, mtry_i)
}
}
```

@@

**Q10.2**
